An Expanded Search for Supernova Remnants in NGC\,6946

### 2018-12-11 ms.tex
Material on coincidences

\todo[inline]{We need a more complete discussion of MF97 and our results.  Possibly this is something wpb could do.  WPB: possibly, if it can wait until I return.  The above paragraph says both "4" and "5" MF objects were observed spectroscopically, so this needs to get cleaned up.}

\todo[inline]{Add comparison here to X-ray sources and to radio SNRs from earlier Lacey paper and also Bruursema+ (2014)}

As shown in Fig.\ \ref{fig_s2_ratio}, the ratios of [SII]$\lambda$6717:SII]$\lambda$6731 for the SNR candidates cluster around the low density limit of 1.4, and from the fact that just about as many objects have nonphysical ratios above 1.4 as below, suggests that the all of the objects are close to this limit.  In the absence of SNR dieameters, we cannot search for trends with diameter, as were seen in M33 (L18) and M83 \citep{winkler17}.

@@

>>>>

\todo[inline]{We need a more complete discussion of MF97 and our results. MF-016 probably needs several sentences as it is a unique object. Possibly this is something wpb could do.  WPB: possibly, if it can wait until I return.  The above paragraph says both "4" and "5" MF objects were observed spectroscopically, so this needs to get cleaned up.}

As shown in Fig.\ \ref{fig_s2_ratio}, the ratios of [SII]$\lambda$6717:SII]$\lambda$6731 for the SNR candidates cluster around the low density limit of 1.4, and from the fact that just about as many objects have nonphysical ratios above 1.4 as below, suggests that the all of the objects are close to this limit.  In the absence of SNR diameters, we cannot search for trends with diameter, as were seen in M33 (L18) and M83 \citep{winkler17}.

@@

\subsection{SNR candidates in NGC6946 in Other Wavelength Bands}

\todo[inline]{Add comparison here to X-ray sources and to radio SNRs and to Fe II objects. ksl - It's not clear this is quite at the right place in the text. It depends a bit on whether there is anything special about the objects we have identified.}

Searches for SNRs in NGC6846 have been carried out in several other wavelength ranges.  In particular,  \cite{lacey01} identified 35 radio sources as SNR candidates on the facts that these sources had non-thermal spectral indices and were positionally coincident with \ha\ emission.  As one might expect these objects are located mostly in the spiral arms of NGC6946 where there is active star formation and where one might expect SNe to explode.  There are seven emission nebulae in our list of SNR candidates that lie within 2 arcsec of radio SNR candidates; this is five more than had been identified previously, but a small fraction of the total number of radio objects.  As an alternative to using the [SII]:\ha\ ratio to identify SNRs in an external galaxy, \cite{bruursema14}  carried out interference filter imagery of NGC6946 in the light of [FeII]1.64$\mu$.  H II regions are expected to have little if any [Fe II], so detection of an emission nebula with [Fe II] is a strong indication of shock heating.  Noting some concerns about the quality of the data,  \cite{bruursema14}  identified 48 candidate objects, only three of which, L19-076, L19-095=MF-014, L19-098=MF-016, are in our sample of objects.

SNRs are also X-ray sources and therefore we have also looked to see how many X-ray sources in NGC6946 could be found in our candidate lists.  The most detailed X-ray study of  NGC6946 to date was carried out by \cite{fridriksson08} using Chandra, who constructed a catalog of 90 point sources, of which 25 appeared to be time variable (and hence likely X-ray binaries).  Of the 90 point sources, there are eight which are positionally coincident,

\todo[inline]{One should probably look further into the X-ray coinidences.  How many of the identified sources were time variable.  Also, MF-016 which is one of the sources is a special case.}
